Geometric variational problems

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have show that energies derived from
molecular dynamics and \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the
membrane thickness, membrane energy is well-characterized by the
Canham-Helfrich energy used throughout the fluid-structure literature
\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
  qua-bir2014, qua-vee-you2019}.
%\todo[inline]{YNY: place your recent works here}
The Canham-Helfrich energy is actually a special case of
\eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
orientation) and collapsing both monolayers onto the membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.

>>>>

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the
membrane thickness, membrane energy is well-characterized by the
Canham-Helfrich energy used throughout the fluid-structure literature
\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
  qua-bir2014, qua-vee-you2019}.
%\todo[inline]{YNY: place your recent works here}
The Canham-Helfrich energy is actually a special case of
\eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
orientation) and collapsing both monolayers onto the membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.
